The Evolution of Phenotypically Invariant Genetic Networks

### 2017-12-06 kalman_walk_paper.tex
changed Frobenius to Euclidean distance
changed Euclidean distance to equation
changed constant

  \begin{figure}[H]
  \label{fig:osc_incompat}
    \centering
    %\begin{tabular}{cc}
    %\includegraphics[width=0.4\textwidth]{figures/f1_quartic2} &
    %\includegraphics[width=0.4\textwidth]{figures/f2_quad2}
    %\end{tabular}
    \includegraphics[width=0.5\textwidth]{examples/F2_vs_F1_divergence_tau0}
   % \caption{
    %\textbf{(left)} 
    \caption{Phenotype distance to optimum, $D$, using $\rho(t) = \exp(-t/4\pi)$
    for $F_1$ (black) and $F_2$ (blue) hybrids between an $A(0)$ and an $A(\epsilon)$ parent. Genetic distance is computed as the Frobenius norm between two systems.}
    %\textbf{(right)} Same, but for $F_2$ offspring (one line per type of $F_2$).
    %\plri{make this $D$ not $D^2$ and say which line is the overall average $F_2$.
    %}
    \label{fig:osc_incompat}
  \end{figure}
\end{example}

@@

How does this prediction depend on the system size and constraint?
If there are $p$ trait dimensions, constrained in $q$ dimensions,
and if $\omega$ is proportional to $p-q$,
% the rate that hybrid variance increases with separation between parentals, $\omega$,
% is in some cases proportional to $p-q$, 
then the rate that $F_2$ fitness drops is, roughly,
$(1 + 4 (p-q) C T/N_e)^{-q/2} \propto q (p-q)$, where $C$ is a constant.
Both degree of constraint and number of available neutral directions
affect the speed of accumulation of incompatibilities --
more unconstrained directions allows faster system drift,
but more constrained directions implies greater fitness consequences of hybridization.
However, note that in real systems, it is likely that $\gamma$ also depends on $p$ and $q$.

>>>>

  \begin{figure}[H]
  \label{fig:osc_incompat}
    \centering
    %\begin{tabular}{cc}
    %\includegraphics[width=0.4\textwidth]{figures/f1_quartic2} &
    %\includegraphics[width=0.4\textwidth]{figures/f2_quad2}
    %\end{tabular}
    \includegraphics[width=0.5\textwidth]{examples/F2_vs_F1_divergence_tau0}
   % \caption{
    %\textbf{(left)} 
    \caption{Phenotype distance to optimum, $D$, using $\rho(t) = \exp(-t/4\pi)$
    for $F_1$ (black) and $F_2$ (blue) hybrids between an $A(0)$ and an $A(\epsilon)$ parent. Genetic distance is computed as 
    %Frobenius norm
    %Euclidean distance
    $\sqrt{\sum_{ij} (A_{ij}(0) - A_{ij}(\epsilon))^2}$
    %between two systems
    .}
    %\textbf{(right)} Same, but for $F_2$ offspring (one line per type of $F_2$).
    %\plri{make this $D$ not $D^2$ and say which line is the overall average $F_2$.
    %}
    \label{fig:osc_incompat}
  \end{figure}
\end{example}

@@

How does this prediction depend on the system size and constraint?
If there are $p$ trait dimensions, constrained in $q$ dimensions,
and if $\omega$ is proportional to $p-q$,
% the rate that hybrid variance increases with separation between parentals, $\omega$,
% is in some cases proportional to $p-q$, 
then the rate that $F_2$ fitness drops is, roughly,
$(1 + 4 (p-q) K T/N_e)^{-q/2} \propto q (p-q)$, where $K$ is a constant.
Both degree of constraint and number of available neutral directions
affect the speed of accumulation of incompatibilities --
more unconstrained directions allows faster system drift,
but more constrained directions implies greater fitness consequences of hybridization.
However, note that in real systems, it is likely that $\gamma$ also depends on $p$ and $q$.
